Pomace: a Grappa for Non-Volatile Memory

### 2012-12-11 doc/nvm2013/paper.tex
narrow margins to fit on two pages
a few fixes

\title{Pomace: a Grappa for Non-Volatile Memory \vspace{-.2in}}
\authorinfo{Jacob Nelson$^{\dagger}$,
  Brandon Holt$^{\dagger}$,
  Brandon Myers$^{\dagger}$,
  Preston Briggs$^{\dagger}$,
  Luis Ceze$^{\dagger}$,
  Simon Kahan$^{{\dagger \ddagger}}$,
  Mark Oskin$^{\dagger}$
}{\textdagger University of Washington, \textdaggerdbl Pacific Northwest National Laboratory}{
  \{nelson, bholt, bdmyers, preston, luisceze, skahan, oskin\}@cs.washington.edu \vspace{-1in}
}

\maketitle
\begin{abstract}
We revisit Grappa, our software platform that scales in-memory irregular
applications on commodity clusters.
We contemplate options for adapting Grappa to use non-volatile memory technologies.
\end{abstract}
\vspace{-.1in}

@@

@@

\item[Distributed shared memory.] Our DSM system provides support for
fine-grain access to data anywhere in the system. It supports synchronization
operations on global data, explicit local caching of any memory in the system,
and support for operations on remote data (delegating operations to owner node).
By tight integration with the tasking system and the
communication layer, our DSM system offers high aggregate random
access bandwidth to remote data.

@@

Grappa thus facilitates
expression of fine-grained task parallelism at the application
programming level, employing that concurrency as needed to sustain throughput in the presence of long latency operations and to better utilize commodity networks.  Programmers attend only to expressing the parallelism in their program, not to scheduling it.  While similar latency
tolerance and aggregation techniques can be manually coded into some
applications, Grappa relieves the programmer of this burden.  In
addition, Grappa provides an API for reader-writer lock semantics for the
purpose of manipulating a local copy of any contiguous portion of the
shared address space, enabling programmers to exploit spatial and
temporal locality while maintaining a consistent global view.  With
these features, we have demonstrated performance on commodity systems
for highly irregular applications approaching that of the Cray XMT, a
fully custom system.

>>>>

\title{Pomace: a Grappa for Non-Volatile Memory}
\authorinfo{Jacob Nelson$^{\dagger}$,
  Brandon Holt$^{\dagger}$,
  Brandon Myers$^{\dagger}$,
  Preston Briggs$^{\dagger}$,
  Luis Ceze$^{\dagger}$,
  Simon Kahan$^{{\dagger \ddagger}}$,
  Mark Oskin$^{\dagger}$
}{\textdagger University of Washington, \textdaggerdbl Pacific Northwest National Laboratory}{
  \{nelson, bholt, bdmyers, preston, luisceze, skahan, oskin\}@cs.washington.edu}

\maketitle
\begin{abstract}
We revisit Grappa, our software platform that scales in-memory irregular
applications on commodity clusters.
We contemplate options for adapting Grappa to use non-volatile memory technologies.
\end{abstract}

@@

\item[Distributed shared memory.] Our DSM system provides support for
fine-grain access to data anywhere in the system. It supports synchronization
operations on global data, explicit local caching of any memory in the system,
and support for operations on remote data (delegating operations to home node).
By tight integration with the tasking system and the
communication layer, our DSM system offers high aggregate random
access bandwidth to remote data.

@@

@@

Grappa thus facilitates
expression of fine-grained task parallelism at the application
programming level, employing that concurrency as needed to sustain throughput in the presence of long latency operations and to better utilize commodity networks.  Programmers attend only to expressing the parallelism in their program, not to scheduling it.  While similar latency
tolerance and aggregation techniques can be manually coded into some
applications, Grappa relieves the programmer of this burden.  In
addition, Grappa provides an API for reader-writer semantics for the
purpose of manipulating a local copy of any contiguous portion of the
shared address space, enabling programmers to exploit spatial and
temporal locality while maintaining a consistent global view.  With
these features, we have demonstrated performance on commodity systems
for highly irregular applications approaching that of the Cray XMT, a
fully custom system.
